---
title: "Webinar- spatial model"
author: "Alonzo"
date: "5/27/2020"
output: 
    prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: latex
---

```{r setup, include=FALSE}
rm(list = ls());gc()
pacman::p_load(data.table,dplyr,spdep,spatialreg,readr, sf, tmap, stringr,tidyr,ggplot2,plotly,corrplot)
Sys.setlocale("LC_ALL","Chinese (Traditional)_Taiwan.950")
options(scipen=7)
load("D:/Desktop/Econometrics2/Econometrics2/Webinar/hen.rdata")
load("D:/Desktop/Econometrics2/Econometrics2/Webinar/GeoTW108.rdata")
load("D:/Desktop/Econometrics2/Econometrics2/Webinar/K.rdata")
load("D:/Desktop/Econometrics2/Econometrics2/Webinar/RiTW108.rdata")
```

## Spatial Model Demo

* 通常OLS不會考慮空間的特性，當然有些時候學者會運用虛擬變數來代表美國的不同地區 <br>
例如東北方、西南方、西部地區等等，但大部分不考慮空間因素例如失業率，<br>
個人收入，社會資本以及一些隨機因素等，這些鄰近的州有可能造成的影響。<br>

* 從空間模型來看，所謂的鄰居 可以定義是方圓500哩內 設定一個圈圈bubble <br> 然後可以知道哪些是鄰居，或者以距離來設定強弱權重，比較近的是strong neighbor <br> 這樣，因此我們可以從三種角度來思考相鄰州別可能的影響。<br>


## Checking the data

```{r}
colnames(K)
names(Income)[2] <- "V_ID"
Income <- filter(Income, 資料時間=="106Y")
K <- left_join(K,Income[,c(2,12)], by="V_ID")
names(K)[27] <- "Income"
```

* P_DEN: 人口密度 <br>
  M_F_RAT: 性別比 <br>
  FLD1: 扶養比 <br>
  FLD2: 扶幼比 <br>
  FLD3: 扶老比 <br>
  FLD4: 老化指數 <br>
  Income: 106年所得中位數 <br>
  Delta: 得票率差 <br>

## Correlation of IV & DV

```{r }
n <- c("P_DEN","M_F_RAT","FLD1","FLD2","FLD3","FLD4","Income","Delta")
KK <- select(K,all_of(n))
KK$geometry <- NULL
KK<- na.omit(KK)
KK$Delta <- abs(KK$Delta) # 取絕對值
pairs(Delta~P_DEN+FLD1+FLD2+FLD3+FLD4+Income+M_F_RAT,data=KK,
      main="Simple Scatterplot Matrix")
M <- cor(KK)
corrplot(M)
```




## Spatial Model expression

* (A) The value of X's in a region might affect (or be related to ) the value of y in a neighboring region (lag X) <br>

$$\mathrm Y= X\beta+WX\theta+\varepsilon$$

## Make the weights matrix


$$
W=
\left[
\begin{matrix}
 W_{11}      & W_{12}      & \cdots & W_{1n}      \\
 W_{21}      & W_{22}      & \cdots & W_{2n}      \\
 \vdots & \vdots & \ddots & \vdots \\
 W_{n1}      & W_{n2}      & \cdots & W_{nn}      \\
\end{matrix}
\right]
$$



```{r}
KK <- select(K,all_of(n));KK$Delta <- abs(KK$Delta); KK <- na.omit(KK)
queen.nb=poly2nb(KK)
queen.listw=nb2listw(queen.nb)
listw1= queen.listw
```

## OLS Model

```{r}
reg.eq1=Delta~P_DEN+M_F_RAT+FLD1+FLD2+FLD3+FLD4+Income
reg1=lm(reg.eq1,data=KK)
summary(reg1)
```

## Spatially Lagged X (SLX) Model

```{r}
reg2=lmSLX(reg.eq1,data=KK, listw1)
summary(reg2)
impacts(reg2,listw=listw1)
```

## Spatial Autoregressive (SAR) Model

* (B) The value of y in a region might affect (or be related to ) the value of y in a neighboring region (lag y) <br>

$$\mathrm Y=\rho WY+X\beta+\varepsilon$$

```{r}
reg3=lagsarlm(reg.eq1,data= KK, listw1)
summary(reg3)
impacts(reg3,listw=listw1)
```

## 「The work of science is to substitute facts for appearances，and demonstrations for impressions. —— John Ruskin」
